Transforming Trash as an Artistic Act

### 2015-12-16 chapter2_reduced.tex
Chapter review
Former-commit-id: f64723a83902ea5f39ee5e85800eba6ae02dbc92

%
%
In this chapter trash and the practice of transforming trash is examined in theoretical and conceptual aspect. Theoretical foundations of trash (Rubbish Theory) are discussed. Beyond common perception and dictionary meaning of trash alternative or different approaches are examined with the help of ideas of philosophers (Zizek). Focused on the type of trash (disposable, single-use trash) and questioned the behavioural pattern that generates mountains of trash with these disposable trash. Further it is mentioned how artist are approached to these notions and how their work viewed from offered window (or theoretical and conceptual framework).

%
%
\section{Throw away culture}
Firstly we need to ask what is the source of trash. How is it generated? Secondly what are the behaviors behind the producing trash?

%
%
\summary{Disposable items}
\comment{Disposable: made to be used once or only a few times. Made to be thrown away after one use or several uses. Not permanent or durable. Not designed to reuse again and again. For examples packages of bevarages, paper cups etc. They are used very short-time. Their lifetime can be measured in minutes in terms of usage.  However their usage durations are very short, they continue to exist in the nature.} \todo{transition gerekli.} \paraphrase{The strange think about many products that are produced these days is that they are not made to last for a long time.} \todo{ref.}

% In light of this argument,

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\summary{Life an object} 
\paraphrase{One could claim that the end of the life of an object corresponds to the moment in which it is disposed of. This disposal might take place in different forms and for different reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste. In this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\summary{Consumerism} 
\paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new. The capacity for serial replacement is also the capacity to throw away without concern.”} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

\summary{Capitalism, market} 
The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap. They were designed to decrease in value over time - to be used one, or twice and than to be thrown away. This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products. \todo{Waste and wantta bununla ilgili bir bölüm olmalı.}

\summary{Initial function} 
When an object is discarded it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of coca cola consumed, its initial function is fulfilled and it is intended to be thrown out as trash.

\paraphrase{being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid (Hawkins 2006: x)}

@@

% Reference from Identity, mobility and the throwaway society
\summary{The term throwaway culture} 
Life magazine first introduced the term "throw-away" mentioning that behavioral pattern of society \todo{life magazine tekrar bak.}. \comment{Scholars argue that contemporary societies are throwaway societies (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003) \todo{ref required.}.} The term is actually a criticism of over consumption of short-live disposable objects. \comment{The term over consumption refers to a way of living in which the lifestyle patterns of human beings lead to an accelerated expenditure of natural resources.} \paraphrase{Importantly the term throw away society has a slightly negative connotation, or meaning. When you describe a society as a throw away society, you are probably criticizing that behaviors or showing your disapproval.}

\paraphrase{Life magazine fashionably heralded the advent of the "throwaway society" in 1955. 1971 daniel ingersoll reporting on his findings in the journal man in the notheast, "the industrial revolution ... was supplying the customer with hundreds of disposable containers and materials by the end of the nineteenth century. the estimated 25.000 cubic yards of fill deposited in the upper portion of puddle dock show that the age of the throw away world began not in the twentieth century but during the nineteenth."} \todo{ref. Hangi kaynaktan?}

% Reference from Identity, mobility and the throwaway society
\summary{Counter-argument} 
According to conducted a qualitative research people are really do not throw away their things. People are not wasteful as claimed. However, \paraphrase{the research did not include the leftovers and detritus of food consumption packaging, bottles, and food waste, for example and neither was it concerned with another major category contributor to the volume of household waste, those `disposable' goods that are the primary means to maintaining bodily hygiene and cleanliness (Shove, 2003)}. They analyzed the things like television, furniture and toys like that. Therefore their result showed that people are not so wasteful as claimed when considering durable items. However in this thesis scope, the focus is disposable items and it can be mentioned the wastefulness of society. \todo{bu kısmı adam et.}

\summary{Consumer culture}
\paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these thesis are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century. In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2).} \todo{find exact ref.}

%
%
\summary{Factors that cause over-consumption habits}
Technological advancements can be one of them. These items with the help of industrialization can be produced easily. Mass production. Disposable items are reduces the labor and human resources as compared to the traditional ways (Consider napkin vs wipes, glass vs paper cup). Another point is that they are more affordable in terms of supply chain and cost. In other words you can put new one easily. Therefore there is no need to save the old one. Last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private.} \todo{ref. ontology of trash}

\paraphrase{Taken to its obsessive extreme, the germ theory proscribes companionship. The Latin root for this word, cum pani, literally means to share bread. But insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self. Safety in a world of bacteria implies isolation. Packaging successfully isolates both food and consumer within a structure of sterile control. In essence, it encloses the commons. Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.} \todo{ref. ontology of trash}

\begin{quote}
While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travellers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
\end{quote}

\summary{Dark side} 
Usage of disposable items in the society is very widespread. For same cases it is inevitable. Beyond the advantages of disposable items there are side of effects of consuming them excessively. They result in mountains of garbage.

\comment{Handling of mountains of garbage is another topic. It is not the topic of this thesis. It is not debated that usage of disposals are supported or not supported. It might be subject of another thesis. What is important here the results of it and the reflection of the artist.} \comment{Buna karşı geliştirilen bir refleks olduğu için bu kısma giriyorum. Aynı zamanda ben de bu ürünü kullanıyorum. Konuyu o yüzden farklı açılarından anlamak gerekli.}

%
%
\summary{Art}
There are some artists whose works are related with the phenomena expressed above. (Some of the works of artist can be examined in this phenomena.) Not every people throw away disposable objects, some of them save them and use for their own purposes.

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Caps Seurat, 2011 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

Chris Jordan creates digital photographic series that turns numbers to visuals. Provide different way to understand the statistics and the missed reality of consumerism. Creates gigantic prints to express numbers in a visual manner. Draws attention the the global consumerism. reveals the reality that is hard to understand. Because it is spread to the community and time.

\paraphrase{Portraits of Global Mass culture from Chris Jordan. Depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute. In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.}

\summary{Analysis}
Visuals of Chris Jordan are like modern versions of mosaics. In the age of consumption the most easily accessible material is trash. Trash has different colors and sizes and shapes. Therefore it is a perfect material to build sculptures from them. There is a great diversity of trashes and offers new alternatives.

@@

\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations—the artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Endeavour of re-purposing recycled and found materials.} \todo{cite website}

\summary{Analysis}
This work is for fathers day. Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day). Trashes transformed to diaries. Trash is every where, already at hand.

@@

\paraphrase{I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation and memories of a social moment upcycled from the detritus of our throw-away caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. And on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. But as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. paintings on paper coffee cups displayed as installation in public window spaces. She publicly draw their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects she draw with other people. and so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transform its cup.} \todo{cite her website}

\summary{Analysis}
Inside of glass window. Public space. As she drinks her coffee publicly, also paints them publicly. \todo{related with Liz Parson's argument: practice of trash to durable.}

%
%
\todo{transition needed.} [TRASH and POTRAIT OF PEOPLE] Trash tells about societies and also reveals personal aspects of people's life. What people consume is actually tells many things about them (their choices, possessions etc.) \todo{ref.}. As scholars mentioned that throughout the discards of someone else many thing can be understand. They are end product of our activities and it can be traced through the discard and garbage.

@@

\paraphrase{the work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artefacts and garbage, exploring the function of trash as a resource for understanding cultural and social practice. At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene. (from Trash Culture)}

\todo{transition required.} With the help above understanding of trash, what can we see the work of arts?

@@

\paraphrase{Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. Around her there are pieces of junks speared all over the room. We can understand from her junk what type of life her has. We enter the world of artist through the her trashes.} \todo{Hastalık dönemi... Sanattaki yerine bakmak gerekli.}

%
%
\section{Zizek's Approach to Rubbish}
\todo[inline]{transition required.} 
Last decades there is increasing attention the ecology and rubbish. This section is related to the increasing interest in ecology. Global warming is one of them, plastic pollution on the oceans also is part of it. These types of news and talks increasingly find a place on media more and more. At this stage, Zizek comments on ecology and trash conversely.

% TODO new comer
% \paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}

In documentary film, Examined-life, Zizek, dressed as a sanitation man, talks about ecology in the middle of a garbage dump in London. His part starts with these sentence: \quotes{This [garbage dump] is where we should start feeling at home}.

Draws attention to notion of even if trash disappears from our world but not world. It seems as though the thrown out garbage disappears from our world. However, it disappears only from the world of illusions, but still exists in reality. \comment{Getting rid of it is not action of production. It is action of ignorance. It still waits us at somewhere else or the next generations will have to cope with it. Maybe (as Zizek suggest) the first thing to do is accept the trash.}

>>>>

%
%
In this chapter trash and the practice of transforming it is examined in theoretical and conceptual aspect. Referred to the ideas and work of philosophers and anthropologists to establish a better understanding of trash beyond common perception and dictionary meaning of it.

Firstly, focused on the disposable items that are designed to be ended up in waste bin after a single use. Their usage and place are examined in the society and how other artists used and transformed them is analyzed. Further, disposable items are one of the key material used in the thesis project. Therefore, they need to be discussed in detail.

Secondly, looked through the Zizek's comments on ecological perspectives that dominate the approaches on rubbish.

Lastly, through "Rubbish Theory" transformation of trash and its various status as an object category that is not static is examined.

%
%
\section{Throw away culture}

% Life Magazine, 1955, "Throwaway Living", p43
\summary{Throwaway Society} 
Life magazine published an article titled \quotes{Throwaway Living} and proclaimed the arrival of the \quotes{throwaway society} in 1955 \todo{ref}. It is described as behavioral consumption pattern of society based on throwing away objects after use. The article addresses the question of 
% https://nerc.org/news-and-updates/blog/nerc-blog/2014/01/14/throw-away-society
\quotes{why [to] spend valuable time washing and reusing household objects like plates and silverware when they can be inexpensively made of plastic and disposed of after use? \todo{cite}} In fact, the term  \quotes{throwaway society} is a critic of it by mentioning its wastefulness and has a slightly negative connotation.

According to findings of archaeologist Daniel Ingersoll the age of the throwaway world began not in the twentieth century but during the nineteenth. \todo{ref. rathje1992rubbish p41}

On the other hand, scholars have criticized the notion of \quotes{throwaway society} as being insufficient and over generalization of consumer behavior \cite{gregson2007identity}. According to the result of their qualitative research on consumers over two-year people are not as wasteful as claimed when considering household possessions such as television, furniture and toys. However, their research did not include disposable packaging and bottles. Therefore, the act of throwing away can be narrowed down the specific goods.

In this thesis dealt specifically with industrially produced consumer discards and their subsequent transformation. This thesis is necessarily situated at a particular time, place, and sensibility: the consumer culture of the late twentieth century. In its most basic form, consumer culture can be explained, as "the activities and ethics of a society are determined by patterns of consumption" rather than production \todo{ref. Mamiya 1992, 2}.

@@

%
%
\summary{Disposable Items}
Disposable items are made to be thrown away after used once or only a few times. They are not permanent or durable and not designed to reuse again. Packages of beverages, paper cups and tissues are some of them. They are used very short-time. Their lifetime can be measured in minutes in terms of usage. However, their usage duration is very short, they continue to exist in nature.

Many products that are delivered in these days are not designed to last for a long time. As a result, this encourages people to continue throwing goods away instead of repairing and reusing.

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\summary{Life of an Object} 
One could claim that the end of the life of an object corresponds to the moment when it is refused. This action might take place in different forms and for various reasons; however, in the most literal and common sense, the life of an object ends in a trash can in the form of waste. At this moment, the object is left valueless in all the possible meanings of the term value: It can no more serve a function, it can on no account be exchanged for anything else, and it can by no means engage in the processes of signification to connote and endow its user with specific social values. \todo{ref. emgin2012trashion p.63}

% FROM Trashion: The Return of the Disposed by Bahar Emgin
\summary{not only consumerism, mass production plays significant role. In fact mass production promote consumerism.} 
\paraphrase{Referring to the work of Susan Strasser, Hawkins argues that disposal was central to the logic of mass production and hence should not be assessed as only particular to consumerism in the twentieth century: “Mass production of objects and their consumption depends on widespread acceptance of, even pleasure in, exchangeability; replacing the old, the broken, the out of fashion with the new. The capacity for serial replacement is also the capacity to throw away without concern.”} \todo{ref. hawkins2001plastic p.9, emgin2012trashion p.64}

% TODO Waste and Want disposibility p9

\summary{Capitalism, market, encouragement} 
\paraphrase{The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifically designed to end up on the garbage heap. They were designed to decrease in value over time - to be used one, or twice and then to be thrown away. This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products.} \todo{ref. cerny1996recycled}

\summary{Initial function} 
\paraphrase{When an object is discarded, it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of coca cola consumed, its basic function is fulfilled, and it is intended to be thrown out as trash.} \todo{ref. cerny1996recycled}

\summary{Being wasteful}
As stated, being wasteful in the ways we live is encouraged, expected and in many instances impossible to avoid \todo{ref, hawkins2005ethics p.viii} because the cost of repairing objects sometimes is higher than the original one or very close to it. On the other side, it is refused to use because of they are old fashioned even if they are perfectly fine.

%
%
\summary{Factors that cause over-consumption habits}
Technological advancements can be one of them. Disposable items with the help of industrialization can be produced easily. Mass production. Disposable items reduce the labor and human resources as compared to the traditional ways (Consider napkin(tissue, towel) vs. wipes, glass vs. paper cup). Another point is that they are more affordable regarding supply chain and cost. In other words, people can put new one easily. Therefore, there is no need to save the old one. The last but not least increasing attention of hygiene is contributed to the extension of disposables in the market highly. \paraphrase{The commodities of food and drink must be safe, sterile and private \cite{kennedy2007ontologyh}.}

% hygiene and cleanliness (Shove, 2003, Comfort, Cleanliness and Convenience)

\paraphrase{The germ theory proscribes companionship. The Latin root for this word, cum pani, literally means to share bread. However, insofar as each eater harbors untold numbers of hazardous germs, it is safest to keep one’s food strictly to one’s self. Safety in a world of bacteria implies isolation. Packaging successfully isolates both food and consumer within a structure of sterile control. In essence, it encloses the commons. Susan Strasser narrates part of the history of this enclosure through the career of the disposable drinking cup, which appeared in the early years of the twentieth century.} \todo{ref. ontology of trash}

% toilet paper comes here. Factors related with disposable items.

\begin{quote}
While the sanitary advantages of toilet paper might have been obvious, those of the paper cup required a belief in germs. The widespread use of paper cups was a direct result of a public health crusade educating people about the invisible organisms spread by the common drinking cups once standard in public places, especially trains and railroad stations. Manufacturers of paper cups teamed up with public health authorities to campaign for federal and state regulations banning common drinking cups from use in interstate traffic. Succeeding in 1912, they competed for the business of the railroads and train stations\ldots
Disposable paper cups met significant resistance. Most public places offered them in coin-operated dispensers, and some people were not willing to pay for what had once been free. Respectable travelers carried their own cups, available in metal and celluloid in a variety of collapsable and folding designs. Others reused paper cups from the trash or drank out of the public tanks, putting their lips to the faucet or using the cover of the tank as a cup. Some people protested against the vending machines: soldiers smashed paper cup dispensers in Washington’s Union Station during President Wilson’s inauguration in 1913. And some public places installed drinking fountains instead of paper cups dispensers, although at first these, too, were attacked as unsanitary because people could touch the nozzle with their lips.
\end{quote}

\summary{Dark side} 
Usage of disposable items in the society is very widespread. For same cases it is inevitable. Beyond the advantages of disposable items, there are side effects of consuming them excessively. They result in mountains of garbage.

Handling of mountains of garbage is another subject and will not be discussed in this thesis. It is not claimed that whether usage of disposals is supported or not. It might be subject to another thesis. What is important here understanding the place of garbage for the people and the reflection (approach) of the artist.

%
%
\summary{Art}
There are some artists whose works are related to the phenomena expressed above. (Some of the works of the artist can be examined in this phenomena.) Not every person throw away disposable objects, some of them save them and use for their purposes. They establish some methods to reflect the throwaway culture and its consumption and trash generated patterns.

% ARTWORK
% Portraits of Global Mass culture
\begin{figure}[h!]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_OriginalView.jpg}
  \caption{Original view}
  \label{fig:ChrisJordan_Numbers_CloseView}
\end{subfigure}
\hfill
\begin{subfigure}{.47\textwidth}
  \centering
  \includegraphics[width=\linewidth]{graphics/ChrisJordan_Numbers_CloseView.jpg}
  \caption{Close view}
  \label{fig:ChrisJordan_Numbers_OriginalView}
\end{subfigure}
\caption{Chris Jordan, Caps Seurat, 2011, 60x90" in one panel, and 88x132" in 3 panels}
\label{fig:ChrisJordan_Numbers_CapsSeurat}
\end{figure}

Chris Jordan creates digital photographic series that turns numbers to visuals. He provides a different way to understand the statistics and the missed reality of consumerism. He creates gigantic prints to express the numbers in a visual manner. He draws attention the global consumerism. The work reveals the reality that is hard to capture because of widespread of subject to the community and time.

\paraphrase{Caps Seurat depicts 400,000 plastic bottle caps, equal to the average number of plastic bottles consumed in the United States every minute. It is one of the pieces of Portraits of Global Mass Culture by Chris Jordan is a series of work. In this series, he revisits the statistics of modern societies.  In Running the Numbers, photographer Chris Jordan attempts to convey the vastness of modern consumption by breaking down annual statistics into more graspable quantities depicted by clever visualizations made of individual objects or groups of objects that he photographs. “There’s a disconnect that happens when we assume we know what we’re talking about when we talk about hundreds of millions of plastic bottles,” Jordan says. “I’m trying to translate these numbers from the deadening language of statistics into a visual language that allows some kind of comprehension.” Many of Jordan's works are created from photographs of garbage and mass consumption Jordan uses everyday commonalities such as a plastic cup and defines the blind unawareness involved in American consumerism. His work, while often unsettling, is a bold message about unconscious behaviors in our everyday lives, leaving it to the viewer to draw conclusions about the inevitable consequences which will arise from our habits. He recreates the most remarkable artworks with combining bits of trashes as a mosaic. Here he draw attention to the our consumerism and express them numbers that are very big to understand. All the material that we have is trash to create this pictures.}

\summary{Analysis}
In fact, the work of Chris Jordan is a reproduction of A Sunday Afternoon on the Island of La Grande Jatte which is one of the most notable works of Georges Seurat who was acknowledged as the painter of a post form of Impressionism called Neo-Impressionism. The work accepted as a well-known example of pointilizm that is a technique of painting in which little, individual dots of color are applied in patterns to form an image. This method shows similarities with mosaics of ancient times and pixels of modern times. To make an work from bottle cups with different colors can be related to painting millions of small dots on a canvas. The shape of plastics cups similar to the dots painted onto the canvas so that there could not be a better example of reproduction.

Seurat spent over two years painting A Sunday Afternoon, focusing meticulously on the landscape of the park. However, in our age, it takes only one minute to create the bottle caps that form this painting. In this respect, it reveals the point where society reached.

Visuals of Chris Jordan are like modern versions of mosaics. In the age of mass production and consumption, the most readily available material is trash. It is free and available everywhere, produced every time. Trash has different colors, sizes, and shapes. Therefore, it is a perfect material to build sculptures from them. There is a great diversity of rubbish and offers new alternatives. Nothing is missing with the physical attributes of trash to create visual work.

% Here, sculptures from trash can be added.

@@

\paraphrase{Visual artist and graphic designer Ruby Silvious embarked on a quirky, personal experiment, set to last for 363 days. She decided to repurpose soggy and stained tea bags as unconventional, blank canvases, just waiting to be filled with her artistic expression. The project, entitled 363 Days of Tea, allows Silvious to challenge herself by transforming the recycled material with her intricate illustrations. The artist draws, paints, and forms collages on the salvaged tea bags. This project serves as Silvious’ daily journal, allowing her to record her thoughts and feelings by creating wonderful moody and whimsical designs on little teabag papers. Every day she creates a new piece that reflects her impressions in that moment. Endeavour of re-purposing recycled and found materials.} \todo{cite website}

\summary{Analysis}
This work is for fathers day. Works of Silvious catch the important moments of days and can be as a diary (or a record of that moment and day). Trashes transformed to diaries. Trash is everywhere, already at hand. Small pieces of paper or packages are used as a canvas.

@@

\paraphrase{I began to save all of my coffee cups to use as "canvases" for making art. Transforms coffee cups that are no longer trash but a vehicle for art, ideas, conversation, and memories of a social moment upcycled from the detritus of our throwaway caffeine culture. I like my coffee or tea in a paper take-out cup. Even better than the contents, I like the used cup as a surface on which to draw and paint. Moreover, on the bottom of each one, I write the date, location, occasion and beverage consumed so that every hand-made cup artwork becomes the record of a social moment. Each cup is representing a daily caffeine break. The installation makes visible largely unconscious patterns of consumption; this is what one simple take-away purchase looks like over the course of three years, this is what would usually be thrown away. It can be seen as a measure of time gone by, of money spent, of space to be taken up in a landfill. However, as I upcycle each used cup into an artwork, it becomes the measure of other things as well: an artist's regular habit of generating new ideas, a diary of time spent with friends and colleagues, and the cumulative positive effect of doing something small and manageable every day. There are different versions of it. Paintings on paper coffee cups displayed in open window spaces. She publicly draws their cups (the cup art window installation and public drawing project were on view repeated showed at many places and date. During public drawing projects, she draws with other people. Moreover, so. Buying a beverage is a daily event for Leech (and also many people. These coffee shops all around the world. As she drinks her coffee in the public, she also publicly transforms its cup.} \todo{cite her website}

\summary{Analysis}
She is inside of glass window not white, isolated cube. Glass window provide her to be close to public space. As she drinks her coffee publicly, also paints them publicly. \todo{related with Liz Parson's argument: practice of trash to durable.} There is no difference between them, and also they should not be separated (Why? Trash, production of it, coffee cups are all experienced widespread.). By showing her practice publicly, she encourages other people in order to reconsider trash as a resource to make something. Further she is not only transforming her trash, it is everybody's trash because of everyone uses it.

These three artists mentioned here use disposable items to make their art. Their approach bring another dimension to criticize (or see) the disposable items. New things can be built from them. They can be used for new purposes.

Throwaway culture is a way of producing trash. It is a behavioral pattern, an approach to objects and commodities. Some artists develop different approaches to them. In this type of culture or behavior throwing them is a natural act and promoted. Consumption and wasting things are encouraged. On the other hand, there are examples of saving everything instead of wasting. In the work of Song Dong, "Waste Not" thousands of domestic objects are exhibited. They are owned by his mother and saved for later use. His mother lived a great depression in China, suffered from poorness. She developed the habit of saving things. After died of her husband this habit reached to extreme levels. She saves every tiny little thing. For her trash becomes an essential part of her life. In fact, it not is hard to say that preserved these things are not useless or worthless. She establishes a different relationship with these used objects.

%
%
Trash is much more than what people want to discard. Characteristic of people and societies can be understood from their produced trash.

\summary{TRASH and POTRAIT OF PEOPLE} 
Trash is a reminder of consumption and production activities. In other words, trash is bound to them, and every different of them leaves a diverse range of trash that exposes its type of action. Trash tells about societies choices. What is being left is one of the key things to realize what kind of people, society, action produce it. At one side trash is a produced thing and  What people consume is tells many things about them (their choices, possessions, etc.) \todo{ref.}. As scholars mentioned that throughout the discards of someone else many things can be understood. They are end product of people activities, and it can be traced through the discard and garbage. It is a great example of the approach to the trash is relative and changes from people to people.

"Waste Not" is an exhibit by Chinese artist Song Dong that displays over 10,000 domestic objects formerly owned by his late mother, who refused to throw anything away if she could possibly reuse it.

Song’s mother, Zhao Xiangyuan (1938–2009), was typical of the generation of Chinese who lived through the hardships of the Cultural Revolution in the 1960s and 1970s abiding by the dictum "wu jin qi yong" (waste not). As a result, all commodities owned or collected stockpiled and preserved as protection against future hardship, even in the face of improving economic conditions.

Waste Not is an installation exhibited different locations of the world. This work is a collaboration with the artist’s mother.

\paraphrase{Like many other Chinese at the time, Zhao adopted the habits of frugality and thrift in order to make the best of what little she had. Song recalls that when he was a child, "my mother always brought scraps of fabric to make clothes, because they didn't need to be purchased with the government-distributed clothing coupons." She continued to collect them even in better times because she feared that the shortages might some day return, seeing the habit of "waste not" as a fabao – literally a "magic weapon" to guard against a return to poverty.}

\paraphrase{When Song's father died suddenly in 2002 his mother suffered an emotional breakdown and her habit of holding on to things was taken to extremes, with every possible space of her tiny house crammed with thousands of domestic odds and ends. Song Dong and his sister Song Hui attempted to tidy up for her, but this led to conflict, as Zhao opposed their efforts to dispose of things that she saw as potentially useful. Song eventually came to understand that, as he puts it:}

\begin{quote}
My mother's need to fill space with daily-life objects resulted from a need to fill the emptiness after my father's death. I recognised that in this era of transition, a person could live through several different lives in just one lifetime. In the wink of an eye, one's life could undergo great changes causing deep divisions between old and young.
\end{quote}

Everything that are exhibited here is different than presented on supermarkets. They are not new and not for sale. They represents a way of life. It is common that the exhibition (museum) of famous people's possessions but this work is separated from them as showing ordinary people's objects

For most of people living in western modern societies it is unimaginable to live with all of these items together. However, for Chinese who are faced with same struggles share the emotion and  comment as "It's not [only] your home, it's my home."

Jane Alison, senior curator at the Barbican, said that Waste Not helps us to understand the reality of Chinese history and culture in the 20th century in a way that newspapers can't.

@@

\paraphrase{The work of archaeologists such as William Rathje and Cullen Murphy has offered significant insights into the relationship between archaeological artifacts and garbage, exploring the function of trash as a resource for understanding the cultural and social practice. At the same time, thinkers such as Zygmunt Bauman and Giorgio Agamben have shed light on the fate of the human being as a wasted or discarded element in discourses of socio-political hygiene. (from Trash Culture)}

\todo{transition required.} With the help of mentioned understanding of trash, what can we see the work of arts?

@@

Tracey Emin puts her private life to the public. The work, which Emin now describes as a portrait of a young woman. Around her, there are pieces of junks speared all over the room. We can understand from her junk what type of life she has. We enter the world of the artist through her trashes.

% From wiki
Every detail of her private life is presented through her bed. The idea for The Bed was inspired by a depressive phase in the artist’s life when she had remained in bed for several days without eating or drinking anything but alcohol. The sensation of depression leading to disarray and detritus is not wholly unfamiliar to many people, and The Bed therefore enforces the communicative power that Tracey Emin seeks with her work. The artwork generated considerable media furor, particularly over the fact that the bed sheets were stained with bodily secretions and the floor had items from the artist's room, such as condoms, underwear with menstrual blood stains, other detritus, and functional, everyday objects, including a pair of slippers. The bed was presented in the state that Emin claimed it had been after languishing in it for several days; at the time she was suffering suicidal depression brought on by relationship difficulties.

It is a realization what she did during her depression time. It perfectly represents her condition during days. It can be understood that trash is part of our life. Things that are exhibited in this work are part of her action. She created them and later through them in the mind of people the condition and life of Tracey Emin are recreated.

% Independent http://www.independent.co.uk/arts-entertainment/art/reviews/tracey-emins-my-bed-at-tate-britain-review-in-the-flesh-its-frankness-is-still-arresting-10144882.html
You can interpret it as an uncompromising self-portrait of a woman at a time of emotional trauma – or as a turbulent still life – but it is still a bed and all that a bed symbolizes and encompasses: sleep, sleeplessness, sex in all its manifestations, birth, death and dreams.

Beds meaning also are not same for everyone. It is not just for sleep. Especially for the ones that have small rooms and spaces bed becomes a life space. I have also experienced such a thing at boarding school and university dormitory for total my eight years. Having tight space sometimes bed becomes a place for studying and reading. Sometimes it was used to dry the clothes. It is more than sleeping and provide place for other activities.

% Aslan yattigi yerden belli olur.

%
%
\section{Zizek's Approach to Rubbish}
Last decades there is an increasing attention the ecology and rubbish. Global warming is one of them, plastic pollution on the oceans also is part of it. These types of news and talks increasingly find a place on media more and more. At this stage, Zizek comments on ecology and trash conversely.

\paraphrase{In the late twentieth century, in the context of increasing environmental awareness, this consciousness has altered yet again, and waste has ‘been revalued and recoded from rubbish to recyclable resource, it has moved from the bin to the compost heap, it has insinuated itself into our lives in different ways and with different effects’ (Hawkins 2006: 5).}

In the documentary film Examined-life Zizek dressed as a sanitation man discusses ecology in the middle of a dump in London. His part starts with these sentence: \quotes{This [dump] is where we should start feeling at home}. The place where he talks is a site for depositing people's excess and unwanted material. It is a place of out of sight.
